Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2016-09-30 article/article_for_submission.tex
Adding all changes according to Clementine's review (article for submission)

Then, as an alternative to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
\begin{gather}
\begin{aligned}
\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\underline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_undersu}
\end{gather}
and,
\begin{gather}
\begin{aligned}
\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\overline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_oversu}
\end{gather}
Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp. $I_2$) and minimizing the denominator $I_3-I_4^2$. Analogously, to minimize $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) one minimizes the numerator $I_1$ (resp. $I_2$) and maximizes the denominator $I_3-I_4^2$. As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_u(\vI)$ given the true value of $I_1$.
\begin{figure}[!ht]
\caption{Given the true value of $I_1$, the figure shows in blue the region of all possible values of $\underline{S}_u(\vI)$. There, $\underline{S}_u^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)}$ and $\underline{S}_u^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)}$.}
\centering
\includegraphics[width=.5\textwidth]{Images/estimator_3d_small.pdf}
\label{fig:1}       % Give a unique label
\end{figure}

@@

The failure rates $r_{\delta_{\underline{S}_u}}$ and  $r_{\delta_{\overline{S}_u}}$ of each estimate are evaluated over the $100$ repetitions. These rates are the proportion of the repetitions in which the real errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$.

@@

From the results on these two test functions, the main conclusion is that Variant $A.b$ performs the best. This highlights the efficiency of ``Correlation 2'' to estimate small first-order indices with quasi-Monte Carlo methods. Even if ``Correlation 2'' originally requires more model evaluations, this drawback is completely overridden when this estimator is included into a sequential procedure such as ours.

@@

The discretized Brownian motion $\vect{B}$ follows a multivariate normal distribution with mean $\vzero$ and covariance matrix $\mathsf{\Sigma}$, with $\mathsf{\Sigma}_{ij}=\min(t_i,t_j)$. If $\vect{Y}\sim N(\vzero,I_d)$, given a matrix $M$ such that $\mathsf{\Sigma}=MM^t$, then $M\vect{Y}\sim N(\vzero,\mathsf{\Sigma})$. Hence, we can generate the discretized Brownian motion using the inverse normal cumulative distribution function $\phi^{-1}$: $\vect{B}\sim M\phi^{-1}(\vect{X})$ with $\phi^{-1}(\vect{X})=(\phi^{-1}(X_1),\dots,\phi^{-1}(X_d))^t$ and $\vect{X}\sim \mathcal{U}([0,1]^d)$. Thus, we can estimate the Sobol' indices over $f_{\rm payoff}(M\phi^{-1}(\vect{X}))$. We propose to analyze the results with averaged Sobol' estimates and averaged total number of evaluations over $100$ repetitions. The tolerance $\varepsilon$ and parameters $\ell^*$, $r$ and $\mathfrak{C}(m)$ are set as previously.

Tables \ref{res.AsianChol.Aa}, \ref{res.AsianChol.Ab}, and \ref{res.AsianChol.B} show the results when $M$ corresponds to the Cholesky decomposition of $\mathsf{\Sigma}$. 
\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and total number of evaluations of Variant $A.a$ with Cholesky decomposition.}
%\centering
%\begin{tabular}{ccccc}
%\hline
% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
% $x_3$ & $0.0820$ & $37356$ & $0.3150$ & $65536$ \\ \hline
% $x_4$ & $0.0408$ & $16742$ & $0.1950$ & $33096$ \\ \hline
% $x_5$ & $0.0142$ & $5980$ & $0.0944$ & $16384$ \\ \hline
% $x_6$ & $0.0048$ & $1106$ & $0.0257$ & $1654$ \\ \hline \hline
\centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
 $x_1$ & $0.2120$ & $0.5650$  \\ \hline
 $x_2$ & $0.1370$ & $0.4420$  \\ \hline
 $x_3$ & $0.0820$ & $0.3150$  \\ \hline
 $x_4$ & $0.0408$ & $0.1950$  \\ \hline
 $x_5$ & $0.0142$ & $0.0944$  \\ \hline
 $x_6$ & $0.0048$ & $0.0257$  \\ \hline \hline
\multicolumn{3}{l}{Total number of evaluations: $648 \ 821$} \\ \hline 
\end{tabular}
\label{res.AsianChol.Aa}
\end{table}
\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with Cholesky decomposition.}
%\centering
%\begin{tabular}{ccccc}
%\hline
% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
% $x_3$ & $0.0822$ & $34406$ & $0.3150$ & $65536$ \\ \hline
% $x_4$ & $0.0434$ & $13107$ & $0.1950$ & $33423$ \\ \hline
% $x_5$ & $0.0169$ & $2371$ & $0.0944$ & $16384$ \\ \hline
% $x_6$ & $0.0049$ & $532$ & $0.0259$ & $1577$ \\ \hline \hline
 \centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$  \\ \hline
 $x_1$ & $0.2120$ & $0.5650$  \\ \hline
 $x_2$ & $0.1370$ & $0.4420$ \\ \hline
 $x_3$ & $0.0822$ & $0.3150$  \\ \hline
 $x_4$ & $0.0434$ & $0.1950$  \\ \hline
 $x_5$ & $0.0169$ & $0.0944$  \\ \hline
 $x_6$ & $0.0049$ & $0.0259$  \\ \hline \hline
\multicolumn{3}{l}{Total number of evaluations: $699 \ 487$}\\ \hline 
\end{tabular}
\label{res.AsianChol.Ab}
\end{table}
\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with Cholesky decomposition.}
%\centering
%\begin{tabular}{ccc}
%\hline
% input & $\widehat{\underline{S}}_u$ & $n$ \\ \hline
% $x_1$ & $0.2120$ & $131072$ \\ \hline
% $x_2$ & $0.1350$ & $129766$ \\ \hline
% $x_3$ & $0.0774$ & $62290$ \\ \hline
% $x_4$ & $0.0338$ & $49961$ \\ \hline
% $x_5$ & $0.0149$ & $48845$ \\ \hline
% $x_6$ & $0.0028$ & $17905$ \\ \hline \hline
 \centering
\begin{tabular}{cc}
\hline
 input & $\widehat{\underline{S}}_u$ \\ \hline
 $x_1$ & $0.2120$ \\ \hline
 $x_2$ & $0.1350$ \\ \hline
 $x_3$ & $0.0774$ \\ \hline
 $x_4$ & $0.0338$ \\ \hline
 $x_5$ & $0.0149$ \\ \hline
 $x_6$ & $0.0028$ \\ \hline \hline
\multicolumn{2}{l}{Total number of evaluations: $262 \ 144$} \\ \hline 
\end{tabular}
\label{res.AsianChol.B}
\end{table}
It turns out that Variant $A.b$ does not better than Variant $A.a$. Averaged Sobol' estimates are similar while the averaged number of model evaluations is slightly worse. The explanation is that total effect Sobol' indices require more evaluations than their corresponding first-order indices. As such, ``Correlation 2'' falls into case 1) explained in Section \ref{sec:4.2}. Variant $B$ shows a drastic improvement on the total number of evaluations with the drawback of a false estimation for input $x_4$. Indeed, the discrepancy is higher than $\epsilon$ when comparing with the other two variants.

It is also interesting to see the Sobol' indices estimates when $M$ is constructed with the PCA decomposition. For this case, we only show the results for Variant $A.b$ in table \ref{res.AsianPCA.Ab}.

\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with PCA decomposition.}
%\centering
%\begin{tabular}{ccccc}
%\hline
% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
% $x_1$ & $0.9800$ & $131072$ & $0.9960$ & $117309$ \\ \hline
% $x_2$ & $0.0034$ & $512$ & $0.0172$ & $824$ \\ \hline
% $x_3$ & $0.0004$ & $512$ & $0.0023$ & $512$ \\ \hline
% $x_4$ & $0.0001$ & $512$ & $0.0005$ & $512$ \\ \hline
% $x_5$ & $0.0000$ & $512$ & $0.0001$ & $512$ \\ \hline
% $x_6$ & $0.0000$ & $512$ & $0.0000$ & $512$ \\ \hline \hline
 \centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
 $x_1$ & $0.9800$ &  $0.9960$  \\ \hline
 $x_2$ & $0.0034$ &  $0.0172$  \\ \hline
 $x_3$ & $0.0004$ &  $0.0023$  \\ \hline
 $x_4$ & $0.0001$ &  $0.0005$  \\ \hline
 $x_5$ & $0.0000$ &  $0.0001$  \\ \hline
 $x_6$ & $0.0000$ &  $0.0000$  \\ \hline \hline
\multicolumn{3}{l}{Total number of evaluations: $398 \ 648$} \\ \hline 
\end{tabular}
\label{res.AsianPCA.Ab}
\end{table}
One may conclude that these estimates explain how the PCA Brownian motion construction reduces the high effective dimensionality of the payoff function, in contrast to the initial Cholesky decomposition.

>>>>

Then, as an alternative to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
\begin{gather}
\begin{aligned}
\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\underline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_undersu}
\end{gather}
and,
\begin{gather}
\begin{aligned}
\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\overline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_oversu}
\end{gather}
Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp. $I_2$) and minimizing the denominator $I_3-I_4^2$. Analogously, to minimize $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) one minimizes the numerator $I_1$ (resp. $I_2$) and maximizes the denominator $I_3-I_4^2$. As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_u(\vI)$ given the true value of $I_1$.
\begin{figure}[!ht]
\caption{The delimited region on the figure represents the values $\underline{S}_2$ in $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ for the Bratley \textit{et al.} function. There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$ and $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
\centering
\includegraphics[width=.5\textwidth]{Images/estimator_3d_small.eps}
\label{fig:1}       % Give a unique label
\end{figure}

@@

The failure rates $r_{\delta_{\underline{S}_u}}$ and  $r_{\delta_{\overline{S}_u}}$ of each estimate are evaluated over the $100$ repetitions. These rates are the proportion of the repetitions in which the true estimation errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$. When $\delta_{\underline{S}_u} > \varepsilon$ and $\delta_{\underline{S}_u} > \varepsilon$, we can infer that our integration parameters are not conservative enough and the integrands fell outside the cone \eqref{errbd}.

@@

From the results on these two test functions, the main conclusion is that Variant $A.b$ performs the best. This highlights the efficiency of ``Correlation 2'' to estimate small first-order indices with quasi-Monte Carlo methods. Even if ``Correlation 2'' originally requires more model evaluations, this drawback is completely overridden when this estimator is included into a sequential procedure such as ours. For the case where we are only interested in estimating first-order indices, Variant $B$ should be the best choice as illustrated with the g-function.

@@

The discretized Brownian motion $\vect{B}$ follows a multivariate normal distribution with mean $\vzero$ and covariance matrix $\mathsf{\Sigma}$, with $\mathsf{\Sigma}_{ij}=\min(t_i,t_j)$. If $\vect{Y}\sim N(\vzero,I_d)$, given a matrix $M$ such that $\mathsf{\Sigma}=MM^t$, then $M\vect{Y}\sim N(\vzero,\mathsf{\Sigma})$. Hence, we can generate the discretized Brownian motion using the inverse normal cumulative distribution function $\phi^{-1}$: $\vect{B}\sim M\phi^{-1}(\vect{X})$ with $\phi^{-1}(\vect{X})=(\phi^{-1}(X_1),\dots,\phi^{-1}(X_d))^t$ and $\vect{X}\sim \mathcal{U}([0,1]^d)$. Thus, we can estimate the Sobol' indices over $f_{\rm payoff}(M\phi^{-1}(\vect{X}))$. In this particular application, the choice of $M$ is pivotal to reduce the effective dimensionality of the model. In this regard, Sobol' indices can help us assess whether we reduce the effective dimensionality. We will compare the case with either the Cholesky decomposition and the PCA construction.

We propose to analyze the results with averaged Sobol' estimates and averaged total number of evaluations over $100$ repetitions. The tolerance $\varepsilon$ and parameters $\ell^*$, $r$ and $\mathfrak{C}(m)$ are set as previously.

Tables \ref{res.AsianChol.Aa}, \ref{res.AsianChol.Ab}, and \ref{res.AsianChol.B} show the results when $M$ corresponds to the Cholesky decomposition of $\mathsf{\Sigma}$. 
\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and total number of evaluations of Variant $A.a$ with Cholesky decomposition.}
%\centering
%\begin{tabular}{ccccc}
%\hline
% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
% $x_3$ & $0.0820$ & $37356$ & $0.3150$ & $65536$ \\ \hline
% $x_4$ & $0.0408$ & $16742$ & $0.1950$ & $33096$ \\ \hline
% $x_5$ & $0.0142$ & $5980$ & $0.0944$ & $16384$ \\ \hline
% $x_6$ & $0.0048$ & $1106$ & $0.0257$ & $1654$ \\ \hline \hline
\centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
 $x_1$ & $0.2120$ & $0.5650$  \\ \hline
 $x_2$ & $0.1370$ & $0.4420$  \\ \hline
 $x_3$ & $0.0820$ & $0.3150$  \\ \hline
 $x_4$ & $0.0408$ & $0.1950$  \\ \hline
 $x_5$ & $0.0142$ & $0.0944$  \\ \hline
 $x_6$ & $0.0048$ & $0.0257$  \\ \hline \hline
\multicolumn{3}{l}{Total number of evaluations: $648 \ 821$} \\ \hline 
\end{tabular}
\label{res.AsianChol.Aa}
\end{table}
\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with Cholesky decomposition.}
%\centering
%\begin{tabular}{ccccc}
%\hline
% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
% $x_3$ & $0.0822$ & $34406$ & $0.3150$ & $65536$ \\ \hline
% $x_4$ & $0.0434$ & $13107$ & $0.1950$ & $33423$ \\ \hline
% $x_5$ & $0.0169$ & $2371$ & $0.0944$ & $16384$ \\ \hline
% $x_6$ & $0.0049$ & $532$ & $0.0259$ & $1577$ \\ \hline \hline
 \centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$  \\ \hline
 $x_1$ & $0.2120$ & $0.5650$  \\ \hline
 $x_2$ & $0.1370$ & $0.4420$ \\ \hline
 $x_3$ & $0.0822$ & $0.3150$  \\ \hline
 $x_4$ & $0.0434$ & $0.1950$  \\ \hline
 $x_5$ & $0.0169$ & $0.0944$  \\ \hline
 $x_6$ & $0.0049$ & $0.0259$  \\ \hline \hline
\multicolumn{3}{l}{Total number of evaluations: $699 \ 487$}\\ \hline 
\end{tabular}
\label{res.AsianChol.Ab}
\end{table}
\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with Cholesky decomposition.}
%\centering
%\begin{tabular}{ccc}
%\hline
% input & $\widehat{\underline{S}}_u$ & $n$ \\ \hline
% $x_1$ & $0.2120$ & $131072$ \\ \hline
% $x_2$ & $0.1350$ & $129766$ \\ \hline
% $x_3$ & $0.0774$ & $62290$ \\ \hline
% $x_4$ & $0.0338$ & $49961$ \\ \hline
% $x_5$ & $0.0149$ & $48845$ \\ \hline
% $x_6$ & $0.0028$ & $17905$ \\ \hline \hline
 \centering
\begin{tabular}{cc}
\hline
 input & $\widehat{\underline{S}}_u$ \\ \hline
 $x_1$ & $0.2120$ \\ \hline
 $x_2$ & $0.1350$ \\ \hline
 $x_3$ & $0.0774$ \\ \hline
 $x_4$ & $0.0338$ \\ \hline
 $x_5$ & $0.0149$ \\ \hline
 $x_6$ & $0.0028$ \\ \hline \hline
\multicolumn{2}{l}{Total number of evaluations: $262 \ 144$} \\ \hline 
\end{tabular}
\label{res.AsianChol.B}
\end{table}
It turns out that Variant $A.b$ does not perform better than Variant $A.a$. Averaged Sobol' estimates are similar but the average total number of model evaluations is slightly worse. The explanation is that total effect Sobol' indices require more evaluations than their corresponding first-order indices. As such, ``Correlation 2'' falls into case 1) explained in Section \ref{sec:4.2}. Variant $B$ shows a drastic improvement on the total number of evaluations with the drawback of a false estimation for input $x_4$. Its discrepancy is higher than $\epsilon$ when comparing to the other two variants.

Table \ref{res.AsianPCA.Ab}, shows the results for Variant $A.b$ when $M$ is constructed with the PCA decomposition.

\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.a$ with PCA decomposition.}
\centering
\begin{tabular}{ccccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
 $x_1$ & $0.9800$ & $131072$ & $0.9960$ & $117309$ \\ \hline
 $x_2$ & $0.0037$ & $952$ & $0.0172$ & $824$ \\ \hline
 $x_3$ & $0.0016$ & $517$ & $0.0023$ & $512$ \\ \hline
 $x_4$ & $0.0014$ & $512$ & $0.0005$ & $512$ \\ \hline
 $x_5$ & $0.0005$ & $512$ & $0.0001$ & $512$ \\ \hline
 $x_6$ & $0.0002$ & $512$ & $0.0000$ & $512$ \\ \hline
 \multicolumn{3}{l}{Total number of evaluations: }
 \\ \hline
\end{tabular}
\label{res.AsianPCA.Aa}
\end{table}

\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with PCA decomposition.}
%\centering
%\begin{tabular}{ccccc}
%\hline
% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
% $x_1$ & $0.9800$ & $131072$ & $0.9960$ & $117309$ \\ \hline
% $x_2$ & $0.0034$ & $512$ & $0.0172$ & $824$ \\ \hline
% $x_3$ & $0.0004$ & $512$ & $0.0023$ & $512$ \\ \hline
% $x_4$ & $0.0001$ & $512$ & $0.0005$ & $512$ \\ \hline
% $x_5$ & $0.0000$ & $512$ & $0.0001$ & $512$ \\ \hline
% $x_6$ & $0.0000$ & $512$ & $0.0000$ & $512$ \\ \hline \hline
 \centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
 $x_1$ & $0.9800$ &  $0.9960$  \\ \hline
 $x_2$ & $0.0034$ &  $0.0172$  \\ \hline
 $x_3$ & $0.0004$ &  $0.0023$  \\ \hline
 $x_4$ & $0.0001$ &  $0.0005$  \\ \hline
 $x_5$ & $0.0000$ &  $0.0001$  \\ \hline
 $x_6$ & $0.0000$ &  $0.0000$  \\ \hline \hline
\multicolumn{3}{l}{Total number of evaluations: $398 \ 648$} \\ \hline 
\end{tabular}
\label{res.AsianPCA.Ab}
\end{table}

\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with PCA decomposition.}
\centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $n$ \\ \hline
 $x_1$ & $0.9800$ & $131072$ \\ \hline
 $x_2$ & $0.0037$ & $18422$ \\ \hline
 $x_3$ & $0.0028$ & $7834$ \\ \hline
 $x_4$ & $0.0029$ & $10486$ \\ \hline
 $x_5$ & $0.0017$ & $4613$ \\ \hline
 $x_6$ & $0.0029$ & $9467$ \\ \hline \hline
\multicolumn{2}{l}{Total number of evaluations: } \\ \hline 
\end{tabular}
\label{res.AsianChol.B}
\end{table}

One may conclude that these estimates explain how the PCA Brownian motion construction reduces the high effective dimensionality of the payoff function, in contrast to the initial Cholesky decomposition.
